Synergistic retrievals of ice in clouds from elastic backscatter lidar, Ku-band radar and submillimeter wave radiometer observations

### 2023-05-12 RST/responseReviewers.tex

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{longtable}
\author{Mircea Grecu and John E. Yorks}
\title{Response to Reviewers}
\date{}
\begin{document}
\maketitle

\noindent \textbf{Reviewer 1:}
\noindent\textit{ \textbf{General Summary:}

@@

So the problem is not entirely avoided by relying on “observations” instead of models, as the observations were of 
radar reflectivity, not of ice water contents or particle sizes.}\\
\newline
We agree. We do not consider CloudSat retrievals uncertainty or bias free, but we prefer them because

@@

the retrieval algorithm will almost certainly not perfectly reflect the actual size and shape distributions of ice 
particles around the globe.}\\
\newline
We agree. As described explained above, our  objective was to derive IWC distributions consistent with the observed vertical distribution of

@@

coefficient ai as a function of relative height,” but if that were the case, I would expect there to be many more 
points on the scatter plot (i.e. 18 classes times a certain number of relative height levels, to yield hundreds of points).}\\
\newline
We apologize for the confusion.  The points in figure 2 were derived from a classification of the IWC profiles into 36 classes.  
We initially used 36 classes in the analysis, but
we reduced the number of classes to 18 to make the classification and the Ensemble Kalman Filter more robust.  
For consistency and simplicity in the revised manuscript we derive IWC-Z relationships 
for each CloudSat radar bin, with the bins indexed relative to the freezing level bin.  The relative height is now defined as the distance
between the height of the associated bin relative to the freezing level.  Results are quantitatively similar to those in the initial
submission, especially given that the differences between the current $a$/$N_w$ parameterization and the initial one are smaller than 
the random perturbations in $N_w$ that we introduced in the revised analysis to make the evaluation of the radar retrievals more realistic.\\

@@

\textit{Lines 120-121: How is the data in Fig. 2 used to parameterize Nw as a function of height? Do you fit a line/curve to the 
data in Fig. 2? This needs to be clarified.}\\
\newline
Yes, we fit a line to determine the variation of $ln(a)$ as a function of height and then divide the slope by $(1-b)$ to get the variation of

@@

\newline
Thank you for pointing that out. We corrected it in the revised version of the manuscript.\\
\newline
%\newpage
\clearpage
\noindent \textbf{Reviewer 2:}
\newline \textit{The study investigates the synergy between observations from elastic backscatter lidar, Ku-band radar,

@@

Nonetheless, there are significant conceptual flaws in the study.}\\
\newline
We thank the reviewer for their perspective and constructive suggestions.\\
\noindent \textit{First of all, I can't entirely agree with the study's framing. Currently, 
the study investigates the synergies
achieved by adding lidar and radar observations to radiometer observations. 
However, since the active sensors will likely have a much narrower swath, 
combining these observations will only be possible at
a small part of the radiometer's swath. Given the significantly higher information 
content of the active observations, the more relevant question is: What is the 
benefit of including radiometer observations
when radar and lidar observations are available? Simply showing an added value 
from adding radar
and/or lidar observations to radiometer observations, which is the current main 
conclusion of the paper, is a trivial result.}\\
Although active observations are characterized by much narrower swaths and 
significantly worse temporal sampling, they are nevertheless crucial in process 
studies and the development and validation of products from radiometer-only
observations (\cite{stephens2008},\cite{sano2022},\cite{stubenrauch2021}).  The
particular combination of active and passive observations considered in this
study is justified by the current design of the AOS mission. Specifically,
the Ku-band radar is intended to enable accurate estimates of 
the convective precipitation.  Although it was originally envisioned that AOS would
deploy two Ku-band radars, one in an inclined orbit and one in a polar orbit, currently, only
the inclined orbit is expected to feature a Ku-band radar contributed by 
Japan Aerospace Exploration Agency - JAXA.  
The polar orbit radar will operate at higher-frequencies (Ka- or W-and) and 
have cloud-detecting capabilities (i.e. high-sensitivity), but
will not be able to provide direct observations of intense convective precipitation
due to attenuation. Moreover, the polar radar will have nadir-only capabilities,
while the inclined orbit radar will have a
swath of about 200 km.  Both the polar and inclined orbit radars will operate
in tandem with a lidar and a high-frequency radiometer.  We are interested
in the inclined orbit despite the significantly lower sensitivity of the 
Ku-band radar because the synergistic Ku-band radar, elastic lidar and radiometer
estimates of ice in anvil clouds can be studied jointly with various parameters
(i.e. precipitation intensity, vertical velocities, etc.) characterizing the
convective processes responsible for their creation.  Although 
the polar orbit instruments are likely to enable the derivation of more accurate 
synergistic ice estimates, their severely limited ability to quantify convection
makes synergistic ice retrievals from the combination of instruments studied in
this manuscript relevant to the problem of relating the strength of convection to
the horizontal extent of anvil clouds and their impact on climate \cite{hartmann2016}.
Although the improvement in the ice estimates due to the inclusion of radiometer 
observations may seem trivial, it is rather significant given that neither the
lidar nor the Ku-band radar can provide by themselves accurate and complete 
ice estimates, the lidar
due to attenuation and the radar due to its limited sensitivity and complex Particle
Size Distribution (PSD) variability. \\

@@

%include figure
\begin{figure}
\centering
\includegraphics[width=.31\linewidth]{ResponseFigs/lidarOnly_IWP.png}
\includegraphics[width=.31\linewidth]{ResponseFigs/radarOnly_IWP.png}
\includegraphics[width=.31\linewidth]{ResponseFigs/radiometer_IWP.png}
\includegraphics[width=.31\linewidth]{ResponseFigs/lidarOnly_GC.png}
\includegraphics[width=.31\linewidth]{ResponseFigs/radarOnly_GC.png}
\includegraphics[width=.31\linewidth]{ResponseFigs/radiometer_GC.png}

@@

\textit{4. The introduction's title and first sentence mention "high ice clouds". However, the authors do not provide any 
    information on how the 'high ice clouds' are defined or what distinguishes them from regular ice clouds.}\\
\newline
In AOS terminology, high clouds are convectively generated high clouds \cite{braun2022}. Such clouds are the result of strong vertical mass transport 
from the lower troposphere and horizontal transport in the upper troposphere.  While preponderantly consisting of ice, high clouds may exhibit 
liquid phased hydrometeors. To make it clear upfront that we are not considering mixed-phase clouds in this study, we included ice in the title.
We included clarifying statements on the definition of high-clouds in the manuscript. \\

@@

\textit{4. l. 112 and Fig. 2: Please clarify: Why are there 36 scatter points in Fig. 2.? How is the relative height value 
    of the scatter points derived?}\\
\newline
We initially started with 36 similarity classes and derived (through linear regressions in the log-log space) 
an IWC-Z relationship for each class. The points in Fig. 2 represent 
the coefficients $a$ as a function of the height of the class-average IWC peak for each class. We subsequently reduced the number of classes 
to 18 to make the classification and 
estimation process more robust. However, for consistency and simplicity in the revised manuscript we derive IWC-Z relationships 
for each CloudSat radar bins, with the bins indexed relative to the freezing level bin.  The relative height is now defined as the distance
between the height of the associated bin relative to the freezing level.  Results are quantitatively similar, especially given that the
differences between the current $a$/$N_w$ parameterization and the one used in the initial submission are smaller than the random
$N_w$ perturbations used in the analysis.\\

@@

  \bibitem{sano2022}
  Sanò P, Casella D, Camplani A, D’Adderio LP, Panegrossi G. A Machine Learning
  Snowfall Retrieval Algorithm for ATMS. Remote Sensing. 
  2022 Mar 18;14(6):1467.

  \bibitem{stubenrauch2021}
  Stubenrauch CJ, Caria G, Protopapadaki SE, Hemmer F. 3D radiative heating of 
  tropical upper tropospheric cloud systems derived from synergistic A-Train 
  observations and machine learning. 
  Atmospheric Chemistry and Physics. 2021 Jan 26;21(2):1015-34.

  \bibitem{hartmann2016}
  Hartmann DL. Tropical anvil clouds and climate sensitivity. 
  Proceedings of the National Academy of Sciences. 2016 Aug 9;113(32):8897-9.

  \bibitem{braun2022}
  S. A. Braun, J. Yorks, T. Thorsen, D. Cecil and D. Kirschbaum, 
  NASA'S Earth System Observatory-Atmosphere Observing System, 
  IGARSS 2022 - 2022 IEEE International Geoscience and Remote Sensing Symposium, 
  Kuala Lumpur, 
  Malaysia. 2022, pp. 7391-7393, doi: 10.1109/IGARSS46834.2022.9884029.
